---
pdf_document: default
author: "Arbuda Sivani"
date: "3/20/2022"
output: pdf_document
title: "K-Means Clustering"
---

```{r}
Pharmaceuticals <- read.csv("~/ML/Assignment/Assignment_4/Pharmaceuticals.csv")
library(factoextra)
library(ggplot2)
summary(Pharmaceuticals)
```
```{r}
#A. Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the various choices made in conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s)used, the number of clusters formed, and so on.
Pharma <- na.omit(Pharmaceuticals) #removing the missing values
View(Pharma)
#Using only numerical variables (1 to 9) to cluster the 21 firms
row.names(Pharma) <- Pharma[,1]
Pharma2 <- Pharma[,3:11]
head(Pharma2)
Pharma3 <- scale(Pharma2) #scale all the dataframes's quantitative variables
head(Pharma3)

#Determining the number of clusters

fviz_nbclust(Pharma3,kmeans,method = "wss") + labs(subtitle = "Elbow Method") #Elbow method

fviz_nbclust(Pharma3, kmeans,method = "silhouette") + labs(subtitle = "Silhouette Method") #Silhouette method"

#From the above two methods it is clear that k=5 will be the optimum no.of clusters and it is sufficient to interpret the data variation
set.seed(64060)
k5 <- kmeans(Pharma3,centers = 5,nstart = 25)

k5$centers # for centroids
fviz_cluster(k5, data = Pharma3) #to view the clusters
k5
Distance <- dist(Pharma3, method = "euclidean") # Calculating the distance
fviz_dist(Distance)

fit <- kmeans(Pharma3,5)

aggregate(Pharma3, by=list(fit$cluster),FUN=mean)

Pharma4 <- data.frame(Pharma3,fit$cluster) #mean of all quantitative variables
Pharma4

#Clusterplot
library(cluster)
clusplot(Pharma3,fit$cluster, color = TRUE, shade = TRUE, labels = 2, lines = 0)
```
#B. Interpret the clusters with respect to the numerical variables used in forming the clusters.

Cluster 1 - JNJ, MRK,GSK, PFE

Cluster 2 - AHM, WPI, AVE

Cluster 3 - CHTT, IVX, MRX, ELN

Cluster 4 - AGN, BAY, PHA

Cluster 5 - ABT, WYE, AZN, SGP,BMY,NVS,LLY

#After analyzing the aggregate values of the 5 clusters the following interpretations are made:

Cluster 1: Highest Market_Cap and lowest Beta/PE Ratio

Cluster 2: Highest REV Growth and lowest PE/Asset Turnover Ratio

Cluster 3: Highest Beta/leverage/Asset Turnover Ratio and lowest Net_Profit_Margin, PE ratio and Market_Cap

Cluster 4: Highest PE ratio and lowest Leverage/Asset_Turnover

Cluster 5: Highest Net_Proft_Margin and lowest Leverage

#C. Is there a pattern in the clusters with respect to the numerical variables (10 to 12)? (those not used in forming the clusters)

There is a pattern with respect to the numerical variables (10 to 12) and this is with respect to the Median_Recommendation

In cluster 1 there are equal number of Hold and Moderate Buy median recommendations.

In cluster 2 all the three companies have three different median recommendations i.e.,Strong Buy, Moderate Buy and Moderate Sell.

In cluster 3 it is almost about Moderate Buy median recommendation.

In cluster 4 out of the three companies 2 of them have hold median recommendation

In cluster 5 there are highest Hold median recommendations followed by Moderate Sell

Cluster 1,2&3 are mostly Moderate Buy and Cluster 4&5 are mostly Hold.

#D. Provide an appropriate name for each cluster using any or all of the variables in the dataset. 

The following are the naming conventions for each cluster

Cluster 1 - Moderate Buy Cluster or High Mark_Cap cluster

Cluster 2 - Buy Cluster or High Revenuew Growith cluster

Cluster 3 - Moderate Buy Cluster or High Beta/Asset Turnover cluster

Cluster 4 - Hold Cluster or High PE ratio cluster

Cluster 5 - High Hold Cluster or High Net Profit Margin Cluster


